Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

In practice, clouds complicate the detection of ocean glint because they obscure the underlying surface and are themselves non-Lambertian scatterers. \cite{Zugger_2010} simulated photometric and polarized phase variations for planets including the effects of partial cloud coverage and ocean waves. Although the presence of clouds and atmospheric Rayleigh scattering weaken the signal of an underlying ocean, they again find that oceans are detectable and distinguishable from other sources of polarization. \cite{2010ApJ...721L..67R} compared observations of the Earth's scattering phase curve to comprehensive radiative transfer simulations; they found that the photometric brightening of Earth at crescent phases is mostly due to forward scattering from clouds, with a relatively small contribution from ocean glint.
\citet{Zugger_2011} note that ocean glint is best observed in near infrared opacity windows because of the reduced Rayleigh scattering at long wavelengths. This has the added advantage of minimizing the latitude--albedo effect, which could otherwise be a false-positive for photometric brightening at crescent phases due to glint \citep{2012ApJ...752L...3C}. Most recently, \cite{2019A&A...626A.129T,2022A&A...664A.172T} simulated the photometric and polarimetric signatures of terrestrial planets with inhomogeneous clouds. The bottom line is that a direct imaging mission sensitive to the phase-dependent reflected light photometry and polarization of an  exoplanet could establish its habitability.

@@

In the non-eccentric case (i.e., with a circular orbit and where the coronagraphic mask centred on the star), minimum ($\phi_\mathrm{min}$) and maximum ($\phi_\mathrm{max}$) scattering phase angles accessible are symmetric about 90 degrees (). 
%
We define the angle $\Delta \phi$ such that: 
\begin{equation}
    \label{eq:Delta_phi}
    \Delta \phi 
    = \phi_\mathrm{max} - \phi_\mathrm{min}
    =  2(\phi_\mathrm{max} - 90) 
    =  2(\phi_\mathrm{min} + 90)
\end{equation}

@@

\begin{equation}
    \label{eq:scattering_angle}
    \cos\left(\dfrac{\Delta \phi}{2}\right) = \frac{\mathrm{IWA \cdot d_*}}{a}
\end{equation}

\begin{figure}
    \centering
    \includestandalone{tikz/scattering-angle}
    \caption{
        The on-sky projected planet distance, $r_\mathrm{proj}$, of a planet with a semi-major $a$ at a distance $d_*$. The scattering phase angle, $\phi$, is the angle between the line of sight to the star and the line connecting the star and planet. $\delta$ is the on-sky angular separation as viewed by the observer. \todo{should the red angle be $\phi$?}
    }
    \label{fig:scattering-angle}
\end{figure}

>>>>

In practice, clouds complicate the detection of ocean glint because they obscure the underlying surface and are themselves non-Lambertian scatterers. \cite{Zugger_2010} simulated photometric and polarized phase variations for planets including the effects of partial cloud coverage and ocean waves. Although the presence of clouds and atmospheric Rayleigh scattering weaken the signal of an underlying ocean, they again find that oceans are detectable and distinguishable from other sources of polarization. \cite{2010ApJ...721L..67R} compared observations of the Earth's scattering phase curve to comprehensive radiative transfer simulations; they found that the photometric brightening of Earth at crescent phases is mostly due to forward scattering from clouds, with a relatively small contribution from ocean glint.
\citet{Zugger_2011} note that ocean glint is best observed in near infrared opacity windows because of the reduced Rayleigh scattering at long wavelengths. This has the added advantage of minimizing the latitude--albedo effect, which could otherwise be a false-positive for photometric brightening at crescent phases due to glint \citep{2012ApJ...752L...3C}. Most recently, \cite{2019A&A...626A.129T,2022A&A...664A.172T} simulated the photometric and polarimetric signatures of terrestrial planets with inhomogeneous clouds. The bottom line is that a direct imaging mission sensitive to the phase-dependent reflected light photometry and polarization of an  exoplanet could establish its habitability. \textcolor{blue}{Tighten the above two paragraphs and combine with the following.}

@@

In the non-eccentric case (i.e., with a circular orbit and where the coronagraphic mask centred on the star), minimum ($\varphi_\mathrm{min}$) and maximum ($\varphi_\mathrm{max}$) scattering phase angles accessible are symmetric about 90 degrees. 
%
We define the angle $\Delta \phi$ such that: 
\begin{equation}
    \label{eq:Delta_phi}
    \Delta \phi 
    = \phi_\mathrm{max} - \phi_\mathrm{min}
    =  2(\phi_\mathrm{max} - 90) 
    =  2(\phi_\mathrm{min} + 90)
\end{equation}

@@

\begin{equation}
    \label{eq:scattering_angle}
    \cos\left(\dfrac{\Delta \varphi}{2}\right) = \frac{\mathrm{IWA \cdot d_*}}{a}
\end{equation}

\begin{figure}
    \centering
    \includestandalone{tikz/scattering-angle}
    \caption{
        The on-sky projected planet distance, $r_\mathrm{proj}$, of a planet with a semi-major $a$ at a distance $d_*$. The on-sky angular separation as viewed by the observer is $\delta$. The scattering phase angle, $\varphi$, is the angle between the line of sight to the star and the line connecting the star and planet.  
    }
    \label{fig:scattering-angle}
\end{figure}
